### 2024-03-19 latex/HP1_comm.tex
new files and Nagari-Support for Jyotsna

%%%%%%%%%%
\subsection*{1.24}
\begin{translation}[hp01_024]
While maintaining the wild cock pose, [the yogi] binds the neck with the hands and lies [on his back] upturned like a tortoise. This is the upturned tortoise (\emph{uttānakūrmaka}).
\end{translation}

@@

%%%%%%%%%%
\subsection*{1.27}
\begin{translation}[hp01_027]
Matsyendra's seat is a destructive missile for the many terrible diseases that develop in the stomach; through practice it brings about in people the awakening of Kuṇḍalinī and steadiness of the spine.
\end{translation}

@@

% ?? Mention that the mudrās practised with the breathing techniques are the bandhas (2.44-45) 
%The metre of 1.55c is a \emph{ra-vipulā} with \emph{nāḍi}.%
\end{philcomm}

>>>>

%%%%%%%%%%
\subsection*{1.24}
\begin{translation}[hp01_024]
While in the wild cock pose, [the yogi] binds the neck with the hands and lies [on his back] upturned like a tortoise. This is the upturned tortoise (\emph{uttānakūrmaka}).
\end{translation}

@@

%%%%%%%%%%
\subsection*{1.27}
\begin{translation}[hp01_027]
Matsyendra's seat is a destructive missile for the many terrible diseases that develop in the stomach; through practice it brings about in men the awakening of Kuṇḍalinī and steadiness of the spine.
\end{translation}

@@

% ?? Mention that the mudrās practised with the breathing techniques are the bandhas (2.44-45) 
\end{philcomm}

### 2024-03-19 latex/HP2_comm.tex
new files and Nagari-Support for Jyotsna

Cf. \emph{Satkarmasaṅgraha} 135, 140–141

@@

\begin{philcomm}[hp02_046]
%\emph{madhyapaścimatānena} is possible and well attested.
As is clear in the source text, the \emph{Gorakṣaśataka}, the three techniques alluded to here are \sl{mūlabandha, jālandharabandha} and \emph{uḍḍiyānabandha} respectively (on which see chapter three).
\end{philcomm}

@@

Cf. \emph{Kumbhakapaddhati} 169

@@

Cf. \emph{Gheraṇḍasaṃhitā} 7.10--11

@@

%%%%%%%%%%
\subsection*{2.71}
\begin{translation}[hp02_071]
Now Plāvanī:\\
With his abdomen completely filled with the wind of eructation, which has been turned inwards, [the yogi] floats easily even in deep water, like a lotus leaf.
\end{translation}

>>>>

Cf.~\emph{Satkarmasaṅgraha} 135, 140–141

@@

\begin{philcomm}[hp02_046]
%\emph{madhyapaścimatānena} is possible and well attested.
As is clear in the source text, the \emph{Gorakṣaśataka}, the three techniques alluded to here are \sl{mūlabandha, jālandharabandha} and \emph{uḍḍiyānabandha} respectively (on which see chapter three).

The stem form \emph{brahma} is found in various compounds in the text. We understand it to refer to Brahman, the absolute, in all instances other than \emph{brahmagranthi}, where we take it to mean the deity Brahmā. See Mallinson 2007:205 n.240.
\end{philcomm}

@@

Cf.~\emph{Kumbhakapaddhati} 169

@@

Cf.~\emph{Gheraṇḍasaṃhitā} 7.10--11

@@

%%%%%%%%%%
\subsection*{2.71}
\begin{translation}[hp02_071]
Now plāvanī:\\
With his abdomen completely filled with the wind of eructation, which has been turned inwards, [the yogi] floats easily even in deep water, like a lotus leaf.
\end{translation}
